\chapter{Conclusion}
All the functionalities are currently done but some still need work done to be improved. 
On the client side both the route search functionality and Live Tracking functionalities are done, albeit in a minimalistic way,
the route creation and representation functionality are fully implemented and will only change upon addition of new functionalities.
User authentication, using the google account to authenticate is also completed. 
The Server side is close to complete lacking only (complete) error handling, finish pagination and search algorithm improvement. 

The expectations to this beta version are pretty similar to the current state of the system, however some problems were found configuring the entire system.
One of the first problems encountered was how a route should be defined. Several iterations were made before arriving at the current one. We avoid saying final
because the definition of a route is susceptive to change when new functionalities are implemented.

While implementing the Client Application some problems were encountered when utilizing the Google Maps API, namely the API key and the service's usage. 
Without an account with a credit card associated we were limited to one API call per day, which was limiting our testing capabilities. This was overcome by creating a wallet (offered by the service with an initial value).
The process that is required to create a route was also a problem, there are some considerations to be had due to the nature of a path: where it starts, 
where it ends, if it is circular, if it is doable in a determined time amongst others.
This topic is intertwined with route definition, changes in the definition also change the creation.

The Service had problems initially with the connection to the Database Management System, specifically because the choice of technologies was not the appropriate one, which
forced a shift to a different one. This used valuable time because two different libraries were learned (Spring Data and JDBI) and later Spring Data was discarded.

Some of the final changes might be the global optimization of the system regarding all the functionalities and the core changes might be in the route Search Algorithm that should have the best
possible route suggestions, the route live tracking that should send to the user some notifications to help him go through the route and reliable system tests to ensure that 
everything is working properly. Small adjustments to all functionalities will occur as well to guarantee that the structure and representation are in their best possible state.